---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

## Loading and preprocessing the data
First of all, let's unzip our data to the simple *.csv file
```{r}
unzip("activity.zip")
```
Now we can read our dataset and save it to the variable **data**, identify date column as *date* and see the first rows of our table.
```{r}
data  <- read.csv("activity.csv")
head(data)
```

## What is mean total number of steps taken per day?
Calculating the *sum* of the steps ped day and making a histogram using **ggplot2** for it.  
```{r}
library(ggplot2)
totalStepsData  <- aggregate(steps ~ date, data, sum)
ggplot(totalStepsData, aes(x = steps))+
    geom_histogram(fill = "Green", colour = "Black")
```

Now we have the results for sum of the steps per day and can use it for evaluating the **mean** and **median** values.
```{r}
mean(totalStepsData$steps)
median(totalStepsData$steps)
```


## What is the average daily activity pattern?
Calculating the *mean* of the steps per interval, make a plot for it and finding the interval with max activity in the "%H:%M" format 
```{r}
meanStepsData  <- aggregate(steps ~ interval, data, mean)
ggplot(meanStepsData, aes(x = interval, y = steps))+
    geom_line()
format(strptime(as.character(meanStepsData$interval[meanStepsData$steps == max(meanStepsData$steps)] / 100), "%H.%M"), "%H:%M")
```


## Imputing missing values
Calculating the total number of missing values, creating the new dataset with using mean instead of *NA* values. Ploting the new hist.
```{r}
length(is.na(data$steps))
newData  <- data
newData$steps  <- ifelse(is.na(data$steps), meanStepsData[meanStepsData$interval == data$interval,]$steps, data$steps)
newTotalStepsData  <- aggregate(steps ~ date, newData, sum)
ggplot(newTotalStepsData, aes(x = steps))+
    geom_histogram(fill = "Green", colour = "Black")
```
There is some changes in the central part of our hist.

## Are there differences in activity patterns between weekdays and weekends?

```{r}
newData$weekdays  <- ifelse(weekdays(strptime(newData$date, format = "%Y-%m-%d")) %in% c("Saturday", "Sunday"), "weekend", "weekday")
newMeanData <- aggregate(steps ~ interval + weekdays, newData, mean)
ggplot(newMeanData, aes(x = interval, y = steps, group = weekdays, col = weekdays, fill = weekdays))+
    geom_line() + 
    facet_grid(weekdays ~ .)
```
